### 2023-05-26 main.tex
B
i

\end{enumerate}
To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
% \end{itemize}
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}
 For the sake of notation we denote by 
\begin{equation}
	\begin{split}
		A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
		A_{3}=\left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
{\color{red}Are we missing the prefactor $(N+2x)$?}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes
\begin{equation}\label{cond4A}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
To write its solution we define
\begin{equation}
	\chi^{k_{2},k_{3}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+k_{3})}\right)\in \{2,3\}^{k_{2}+k_{3}}\;:\;\sum_{s=1}^{k_{2}+k_{3}}\delta_{i_{s},2}=k_{2}\right\}
\end{equation}
We introduce the following notation: for any fixed configuration $(i_{1},\ldots,i_{(k_{2}+k_{3})})\in \chi^{k_{2},k_{3}}$ 
\begin{equation}
	\mathcal{A}(i_{1},\ldots,i_{(k_{2}+k_{3})})=A_{i_{1}}A_{i_{2}}\cdots A_{i_{(k_{2}+k_{3})}}
\end{equation}
We introduce $\text{SYM}\left(\chi^{k_{2},k_{3}}\right)$ the \textit{symmetric group} on $\chi^{k_{2},k_{3}}$ and we denote by $\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)$ the permutation of an element of the group. \\
The following expression solves \eqref{cond4A}
\begin{equation}
	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right).
\end{equation}
Indeed
\begin{align}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&= A_{2}\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
\\&+
 A_{3}\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&=
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(2,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&+
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(3,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&=
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \\&=
 	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
\end{align}
where in the up to last equality we used the fact that $i_{1}\in \{2,3\}$. 
\paragraph{Generalization to arbitrary $N$}
For arbitrary $N\geq2$ we have 
\begin{equation}
	\chi^{k_{2}\ldots,k_{N}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+\cdots+k_{N})}\right)\in \{2,\ldots,N\}^{k_{2}+\cdots+k_{N}}\;:\;\sum_{s=1}^{k_{2}+\cdots+k_{N}}\delta_{i_{s},q}=k_{q},\;\forall \in \{2,\ldots,N\}\right\}
\end{equation}

Thus the explicit expression becomes
\begin{equation}
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
\end{equation}
with the same notation as in $N=3$ case. 
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
		\\&
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
	\end{split}
\end{equation}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
\begin{equation}
	\begin{split}
	A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left(2x+N)((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
Therefore we rewrite \eqref{cond4} as 
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
The left-hand-side is 
\begin{equation}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\end{equation}
while, on the right-hand-side we have
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&=
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\end{split}
\end{equation}
and similarly 
\begin{equation}
	\begin{split}
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\\&=
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
	\end{split}
\end{equation}
Therefore,
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&+
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
	\end{split}
\end{equation}
Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.

>>>>

\end{enumerate}
To find the function $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ we must fulfil the conditions \eqref{cond1}, \eqref{cond2}, \eqref{cond3}, \eqref{cond4}, \eqref{cond5}, \eqref{cond6}.
% \end{itemize}
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ using symmetric group}

 For the sake of notation we denote by 
\begin{equation}
	\begin{split}
		A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
		A_{3}=\left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
%{\color{red}Are we missing the prefactor $(N+2x)$?}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. Condition \eqref{cond4} becomes

\begin{equation}\label{cond4A}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
We introduce the following indices
	i_{1}=\ldots=i_{k_{2}}=2\qquad i_{k_{2}+1}=\ldots =i_{k_{2}+k_{3}}=3
Then, we introduce the permutation 
	\sigma(i_{j})=i_{k}\qquad \forall j,k=1,\ldots,k_{2}+k_{3}
We write
	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
where we denoted by $\text{SYM}$ the symmetric group on $\{i_{1},\ldots,i_{k_{2}+k_{3}}\}$.\\
It solves \eqref{cond4A}, indeed
	&A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\\=&A_{2}\frac{k_{2}}{k_{2}}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}\frac{k_{3}}{k_{3}}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	A_{2}\frac{k_{2}}{k_{2}}\frac{1}{(k_{2}-1)!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\\+&A_{3}\frac{k_{3}}{k_{3}}\frac{1}{k_{2}!(k_{3}-1)!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
	\frac{1}{k_{2}!k_{3}!}\left(\sum_{\sigma \in \text{SYM}}k_{2}A_{2}A_{\sigma(i_{2})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}+ \sum_{\sigma \in \text{SYM}}k_{3}A_{3}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}})}A_{\sigma(k_{2}+2)}\cdots A_{\sigma(i_{k_{2}+k_{3}})}\right)
	\frac{1}{k_{2}!k_{3}!}\sum_{\sigma \in \text{SYM}}A_{\sigma(i_{1})}\cdots A_{\sigma(i_{k_{2}+k_{3}})}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
where in the up to last equality we used the fact that the quantity first summation is symmetric with respect to the exchange of $A_{2}$ and thus we have $k_{2}$ equal terms. Similarly, for the second summation using the symmetry with respect to $A_{3}$. \\
This argument can be generalized for $N>2$ species introducing
	G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\frac{1}{k_{2}!\cdots k_{N}!}\sum_{\sigma\in \text{SYM}}A_{i_{1}}\cdots A_{i_{k_{2}+\cdots+k_{N}}}
where we assumed 
	i_{1}=\cdots=i_{k_{2}}=2,\qquad \ldots \qquad i_{k_{2}+\cdots+k_{N-1}}=\cdots=i_{k_{2}+\ldots+k_{N}}=N
To write its solution we define
	\chi^{k_{2},k_{3}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+k_{3})}\right)\in \{2,3\}^{k_{2}+k_{3}}\;:\;\sum_{s=1}^{k_{2}+k_{3}}\delta_{i_{s},2}=k_{2}\right\}
We introduce the following notation: for any fixed configuration $(i_{1},\ldots,i_{(k_{2}+k_{3})})\in \chi^{k_{2},k_{3}}$ 
	\mathcal{A}(i_{1},\ldots,i_{(k_{2}+k_{3})})=A_{i_{1}}A_{i_{2}}\cdots A_{i_{(k_{2}+k_{3})}}
We introduce $\text{SYM}\left(\chi^{k_{2},k_{3}}\right)$ the \textit{symmetric group} on $\chi^{k_{2},k_{3}}$ and we denote by $\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)$ the permutation of an element of the group. \\
The following expression solves \eqref{cond4A}
	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right).
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&= A_{2}\sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 A_{3}\sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2}-1,k_{3}})}\mathcal{A}\left(2,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}-1})}\mathcal{A}\left(3,\sigma(i_{2}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 \sum_{\sigma\in \text{SYM}(\chi^{k_{2},k_{3}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+k_{3})})\right)
 	G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
where in the up to last equality we used the fact that $i_{1}\in \{2,3\}$. 
\paragraph{Generalization to arbitrary $N$}
For arbitrary $N\geq2$ we have 
	\chi^{k_{2}\ldots,k_{N}}:=\left\{\left(i_{1},\ldots,i_{(k_{2}+\cdots+k_{N})}\right)\in \{2,\ldots,N\}^{k_{2}+\cdots+k_{N}}\;:\;\sum_{s=1}^{k_{2}+\cdots+k_{N}}\delta_{i_{s},q}=k_{q},\;\forall \in \{2,\ldots,N\}\right\}

Thus the explicit expression becomes
\begin{equation}
G_{m_{2},\ldots,m_{N},\epsilon}^{k_{2},\ldots,k_{N}}(x)=\sum_{\sigma\in \text{SYM}(\chi^{k_{2},\ldots,k_{N}})}\mathcal{A}\left(\sigma(i_{1}),\ldots,\sigma(i_{(k_{2}+\cdots+k_{3})})\right)
\end{equation}
with the same notation as in $N=3$ case. 
\end{comment}
\subsubsection{Explicit solution for $G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)$ with sums and products}
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=&\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\ldots+i_{(k_{2}+k_{3})}=k_{2}\}}
		\\&
		\prod_{s=1}^{k_{2}+k_{3}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}^{i_{s}}\left\{\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}^{1-i_{s}}
	\end{split}
\end{equation}
We show that it fulfils condition \eqref{cond4}. For the sake of notation we denote by 
\begin{equation}
	\begin{split}
	A_{2}= \left\{(2x+N)\left((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{2}(x)\right\}\\
	A_{3}=\left\{\left(2x+N)((\Lambda_{m_{2},m_{3}}(x)+\epsilon)I-T_{0}(x)\right)^{-1}B_{3}(x)\right\}
	\end{split}
\end{equation}
where the dependence of $A_{2},A_{3}$ on $x$ and $\epsilon$ is understood. 
Therefore we rewrite \eqref{cond4} as 
\begin{equation}
	\begin{split}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)
	\end{split}
\end{equation}
The left-hand-side is 
\begin{equation}
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)=\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\end{equation}
while, on the right-hand-side we have
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)&=A_{2}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+i_{k_{2}}+\cdots+i_{(k_{2}+k_{3})}=k_{2}-1\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&=
\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\end{split}
\end{equation}
and similarly 
\begin{equation}
	\begin{split}
		A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=A_{3}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=2}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
		\\&=
		\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}.
	\end{split}
\end{equation}
Therefore,
\begin{equation}
	\begin{split}
A_{2}G_{m_{2},m_{3},\epsilon}^{k_{2}-1,k_{3}}(x)+A_{3}G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}-1}(x)&=\sum_{i_{1}=1}^{1}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
\\&+
	\sum_{i_{1}=0}^{0}\sum_{i_{2}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+i_{2}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
	\sum_{i_{1}=0}^{1}\ldots\sum_{i_{(k_{2}+k_{3})}=0}^{1}\mathbbm{1}_{\{i_{1}+\cdots+i_{(k_{2}+k_{3})}=k_{2}\}}\prod_{s=1}^{k_{2}+k_{3}}A_{2}^{i_{s}}A_{3}^{1-i_{s}}
	\\&=
		G_{m_{2},m_{3},\epsilon}^{k_{2},k_{3}}(x)
	\end{split}
\end{equation}
Conditions \eqref{cond1}, \eqref{cond5}, \eqref{cond6} are trivially fulfilled. Conditions \eqref{cond2} and \eqref{cond3} are satisfied because $B_{2}(x),B_{3}(x)$ are rising operators.
